---
title: "P8105_hw6_xy2395"
author: "Jack Yan"
date: "11/16/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


## Problem 1

### Data manipulation
 
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  # Create a city_state variable
  mutate(city_state = str_c(city, ", ", state),
         # Create a binary variable indicating whether the homicide is solved
         resolved = as.numeric(disposition == "Closed by arrest")) %>% 
  # Omit some cities
  filter(!city_state %in% c('Dallas, TX', 'Phoenix, AZ', 'Kansas City, MO', 'Tulsa, AL')) %>% 
  # Modifiy victim_race to have categories white and non-white, with white as the reference category. 
  mutate(victim_race = if_else(victim_race == "White", "white", "non-white"),
         victim_race = fct_relevel(victim_race, "white")) %>%
  # Be sure that victim_age is numeric
  mutate(victim_age = as.numeric(victim_age))
  
  str(homicide_df)
```

### Baltimore, MD

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; 
apply the broom::tidy to this object; 
and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing black victims to white victims keeping all other variables fixed.

```{r}
fit_logistic = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())

fit_logistic %>% 
  broom::tidy()  
  
```







Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing black victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.


